### 2020-01-20 ChapterResults/chapterResults.tex
Fixed: Duplicate sentence
Fixed: Removed speeds from end of result graph captions

\section{Collision Correctness Experiments}
In the following section we explore the correctness of collisions between objects, i.e. do objects have the same collision behaviour in a AP as they do in a centralised system. We are concerned with objects that are migrating and/or interacting with an object that has recently migrated.
We will now explain how a naive system can lead to erroneous collision behaviour and AP can lead to erroneous collision behaviour if speed, frame-time or latency go above the user-defined tolerances.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $16m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. }
	\label{fig_CollisionsPenVsSpeedLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $32m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. $32m\mathord{\cdot}s^{-1}$}
	\label{fig_CollisionsPenVsSpeedMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $64m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. $48m\mathord{\cdot}s^{-1}$}
	\label{fig_CollisionsPenVsSpeedHigh}
\end{figure}
	%\label{fig_CollisionsPenVsSpeed}
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{CollisionsPenVsSpeed}
%	\caption{Penetration time of objects with varying relative speed. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. The number and magnitude of errors increases as relative speed increases beyond the tolerance.}
%	\label{fig_CollisionsPenVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{MeanMaxErrorVsSpeed}
%\caption{The mean and max of collision errors with varying relative speed}
%\label{fig_MeanMaxErrorVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{RatiosVsSpeed}
%\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying relative speed}
%\label{fig_RatiosVsSpeed}
%\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $2ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line. }
	\label{fig_CollisionsPenVsLatencyLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $8ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsLatencyMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $16ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line. $48m\mathord{\cdot}s^{-1}$}
	\label{fig_CollisionsPenVsLatencyHigh}
\end{figure}

>>>>

\section{Collision Correctness Experiments}
In the following section we explore the correctness of collisions between objects, i.e. do objects have the same collision behaviour in a AP as they do in a centralised system. We are concerned with objects that are migrating and/or interacting with an object that has recently migrated.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $16m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $32m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $64m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedHigh}
\end{figure}
	%\label{fig_CollisionsPenVsSpeed}
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{CollisionsPenVsSpeed}
%	\caption{Penetration time of objects with varying relative speed. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. The number and magnitude of errors increases as relative speed increases beyond the tolerance.}
%	\label{fig_CollisionsPenVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{MeanMaxErrorVsSpeed}
%\caption{The mean and max of collision errors with varying relative speed}
%\label{fig_MeanMaxErrorVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{RatiosVsSpeed}
%\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying relative speed}
%\label{fig_RatiosVsSpeed}
%\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $2ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsLatencyLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $8ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsLatencyMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsLatencyHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying latency using a latency tolerance of $16ms$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The latency tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsLatencyHigh}
\end{figure}
